Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-09 reports/revision_letter.Rmd
Finish reviewer 1 comments
Closes #13

```{asis r1_2}
The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes? I would want to hear more justification in the manuscript itself on why they assert it is helpful to try and paint them with one broad brush?
```
\WorkInProgress
\todo{Suggestions welcome here}

Our goal with this review was to provide an overview of the field of screen time research.
A summary of the field will, out of necessasity, be more broad that a typical systematic review.
We beleive that there is significant value in providing a single overview to summarise the state of the field.
We have added some additional information to the introduction on this point.

@@

We intended to include the review which best captured the information on the exposure/outcome combination.
The assumption was that the largest review would be the most recent, unless a more recent review had been targeted at a specific population (e.g., those with a disability). 
Manual inspection of the reviews which did not contribute any effects suggests that this heuristic was successful.

\todo{Does anyone know if we based this on a previous review? It's not cited in the registration.}

>>>>

```{asis r1_2}
The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes? I would want to hear more justification in the manuscript itself on why they assert it is helpful to try and paint them with one broad brush?
```

\todo{Suggestions welcome here}

Our goal with this review was to provide an overview of the field of screen time research.
A summary of an entire field will, out of necessasity, be more broad that a typical systematic review.
We beleive that there is significant value in providing a single overview to summarise the state of the field.
We have added some additional information to the introduction on this point:

@@

We intended to include the review which captured the most information on the exposure/outcome combination for each effect size.
The assumption was that the largest review would be the most recent, and that he newer reviews would contain the studies located in previous reviews. 
Manual inspection of the reviews which did not contribute any effects suggests that this was sucessful - older reviews tended to only be included if they focused on the general population while a newer review focused on a sub-population.
